# Date: 2022-01-29
# Author: Someone who ~nows u

# What Explore the East members want

Load data and show the dimensions
```{r}
explore<-read.csv("in/exploreeast.csv")
dim(explore)
```
# Column names
```{r}
colnames(explore)
```

```{r}
tail(explore)
```

## Low attendence is main area of concern
```{r}
table(explore$meetupsAttended)
```

Meetup attendance by percentage
```{r }
# install.packages("ggplot2") # if error
require(ggplot2)
table(explore$meetupsAttended)/dim(explore)[1] 

visitFrequency<-as.data.frame(table(explore$meetupsAttended))
colnames(visitFrequency)<-c("attendances", "count")

bp<-ggplot(visitFrequency, aes(x="",y=count,fill=attendances))+geom_bar(width=1,stat="identity")
pieAttendences <- bp + coord_polar("y", start=0)

pieAttendences
```
Therefore most people who join have never come to any events. Are many bots? 

```{r}

# no differences
```
## Lack of repeat visitors 

## RSVP analysis

# total RSVP Yes'
```{r}
sum(explore$RSVPedYes)
```

from the total of RSVPs
```{r}
sum(explore$totalRSVPs)
```
Are the locations not good

Sort by descending locations
get more than 4 frequency i.e. top 11 values
```{r}
## install.packages("dplyr") # if error
require(dplyr)

locations<-explore %>% count(location, sort = TRUE)
dim(locations)
write.csv(locations, "out/locationsDetail.csv")
head(locations,11)
```

Occupation trade or profession, note there are mis-spellings, dendogram?
```{r}
occupation<-explore %>% count(tolower(whatIsYourOccupationTradeProfession), sort = TRUE)
write.csv(occupation, "occupationsDetail.csv")
head(occupation,11)
```

# hclust?
```{r}
dd <- dist(!is.na(explore$whatIsYourOccupationTradeProfession), method="euclidean")
```

# hobbies or interests
```{r}
# explore interests
head(explore$whatAreYourHobbiesInterests)

tail(explore$whatAreYourHobbiesInterests)
```
```{r}
# remove blanks or NA
sum(explore$whatAreYourHobbiesInterests=="")
# 392/641 ~ 57% are empty string
hobbies<-explore$whatAreYourHobbiesInterests[explore$whatAreYourHobbiesInterests!=""]
```

```{r echo=FALSE}
# separate by commas
# install.packages("stringr") # if error run this
require(stringr)
hobbiesEach<-tolower(str_trim(unlist(str_split(hobbies,","))))

hobbiesAll<-tolower(str_trim(unlist(str_split(unlist(str_split(unlist(str_split(unlist(str_split(unlist(str_split(unlist(str_split(hobbies,",")),';')),'/+')),'/-')),"and")),"//"))))
hobbiesAll<-hobbiesAll[hobbiesAll!='']

# further clean up, as cannot differenciate between 
which(hobbiesAll=="travelling sightseeing eating out museums art galleries theatre")
hobbiesAll<-c(hobbiesAll,tail(unlist(str_split("travelling sightseeing museums art galleries theatre",' ')),5 ))
hobbiesAll<-c(hobbiesAll, "eating out")
hobbiesAll[495] <- "travelling"

which(hobbiesAll=="walking reading rock cooking")
hobbiesAll[452] <-"walking"
hobbiesAll<-c(hobbiesAll,unlist(str_split("reading rock cooking",' ')))

which(hobbiesAll=="walking theatre eating out")
hobbiesAll[94] <- "eating out"
hobbiesAll<-c(hobbiesAll, "walking", "theatre") 

which(hobbiesAll=="travel cook fashion")
hobbiesAll[155] <-"travel"
hobbiesAll<-c(hobbiesAll, "cook", "fashion")

which(hobbiesAll=="tennis anime")
hobbiesAll[93]<-"tennis"
hobbiesAll<-c(hobbiesAll,"anime")
	
which(hobbiesAll=="reading. writing. travelling.")
hobbiesAll[549] <- "reading"
hobbiesAll<-c(hobbiesAll,"writing","travelling")

which(hobbiesAll=="reading. fitness")
hobbiesAll[29] <- "reading"
hobbiesAll<-c(hobbiesAll,"fitness")

which(hobbiesAll=="cooking creative writing travel")
hobbiesAll[632] <- "reading"
hobbiesAll<-c(hobbiesAll,"creative", "writing", "travel")

which(hobbiesAll=="cooking reading")
hobbiesAll[601] <- "reading"
hobbiesAll<-c(hobbiesAll,"cooking")

write.csv(sort(hobbiesAll),"out/hobbiesAll.csv", row.names=FALSE)
```

View list of all hobbies
```{r}
View(sort(hobbiesAll))
```

Hobbies Count
```{r}
hobbiesCount<-table(sort(hobbiesAll))

View(sort(hobbiesCount,decreasing=TRUE))
```

1/5 are travelling, reading 
```{r}

top15Hobbies<-head(sort(hobbiesCount,decreasing=TRUE),15)

top15Hobbies
```
Some interests appear in more than one place 
```{r}
termsTravel<-c("travel in a previous life","travel","travels","travelling","traveling")
length(which(hobbiesAll %in% termsTravel))

termsReading<-c("reading","books","reading books", "a good book!","reading a good articles", "read a lot")
length(which(hobbiesAll %in% termsReading))

termsFood<-c("food","foodie", "eating", "eating out", "good food.", "food & culture")
length(which(hobbiesAll %in% termsFood))

```
```{r}
readingOther<-sum(grepl("read",hobbiesAll))+sum(grepl("book",hobbiesAll))
readingOther
```
```{r}
c(hobbiesAll[grepl("read",hobbiesAll)],hobbiesAll[grepl("book",hobbiesAll)])
```

Out of all travel terms
```{r}
length(which(hobbiesAll %in% termsTravel))/length(hobbiesCount)
hobbiesAll[which(hobbiesAll %in% termsTravel)]
```
# 21% are travel related, 60 in total 
:related terms 7 more explore + 3 for adventure + 1 sightseeing

# Reading
```{r}
readingOther/length(hobbiesCount)
# older method length(which(hobbiesAll %in% termsReading))/length(hobbiesCount)
#old set
hobbiesAll[which(hobbiesAll %in% termsReading)]
```
# 19% are reading related


# Walking & hiking
```{r}
( sum(grepl("walking",hobbiesAll))+sum(grepl("hiking",hobbiesAll)) +sum(grepl("explor", hobbiesAll)) ) / length(hobbiesCount)
sum(grepl("walking",hobbiesAll))+sum(grepl("hiking",hobbiesAll))
c(hobbiesAll[grepl("walking",hobbiesAll)],hobbiesAll[grepl("hiking",hobbiesAll)], hobbiesAll[grepl("explor",hobbiesAll)])
```
# 14 % are walking/hiking related, 32 in total
#:related 3 for adventure

# Reading
```{r}
length(which(hobbiesAll %in% termsFood))/length(hobbiesCount)
hobbiesAll[which(hobbiesAll %in% termsFood)]
```
# 9% are food related, 27 in total

# Soccer / football
```{r}
( sum(grepl("football",hobbiesAll))+sum(grepl("soccer",hobbiesAll)) ) / length(hobbiesCount)
sum(grepl("football",hobbiesAll))+sum(grepl("soccer",hobbiesAll))
c(hobbiesAll[grepl("football",hobbiesAll)],hobbiesAll[grepl("soccer",hobbiesAll)])
```
# 7% are football related, 21 in total

```{r}
top15HobDf <- as.data.frame(top15Hobbies)
colnames(top15HobDf) <- c("interests","Frequency")
ggplot(top15HobDf,aes(x=interests, y=Frequency), s)+
  geom_bar(stat="identity", aes(fill=interests )) + ggtitle("Top 15 not aggregated")
```

# Music

```{r}
hobbiesAll[grepl("music",hobbiesAll)]
```

```{r}
travelling<-length(which(hobbiesAll %in% termsTravel))
#readingOther # reading <-length(which(hobbiesAll %in% termsReading)) # OLDER
walkingHiking<-sum(grepl("walking",hobbiesAll))+sum(grepl("hiking",hobbiesAll))
food <- length(which(hobbiesAll %in% termsFood))
social<-length(c(hobbiesAll[grepl("social",hobbiesAll)],hobbiesAll[grepl("meeting",hobbiesAll)]))
football<-sum(grepl("football",hobbiesAll))+sum(grepl("soccer",hobbiesAll))

xTop5<-c("travelling","reading", "walkingHiking","food", "football")
yTop5<-c(travelling,readingOther,walkingHiking, food, football)
top5 <- as.data.frame(cbind(x=xTop5,y=yTop5))

bpTop5 <-ggplot(top5, aes(x=x,y=y)) + 
  geom_bar(stat="identity", aes(fill=x), color="black")

bpTop5 + scale_fill_hue() +xlab("interests") + ggtitle("Top 5 Hobbies") +ylab("count")
```

# Art
```{r}
termsArt<-c("art","arts","art galleries")
length(which(hobbiesAll %in% termsArt))
```

```{r}
# Want to search for a terms change "coffee" below
term <- "coffee"
hobbiesAll[grepl(term,hobbiesAll)] 

#hobbiesCount<-table(sort(hobbiesAll))

#View(sort(hobbiesCount,decreasing=TRUE))
# last visit common
# lastVisitedGroupOn # CLT
## get max, and min (Today)
```

```{r}
#View(sort(hobbiesAll))
#sort(hobbiesAll)[530]
View(sort(hobbies))
```

Could use stringr and boundary to find words!
